---
title       : Comparisons of the 50 US States
subtitle    : 
author      : ABC
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Data Description

Data for this app comes from the state dataset in R. This dataset contains 50 rows
with statistics from each state, which were gathered in the 1970s. The 8 variables are:

* Population
* Income (per capita)
* Illiteracy (rate)
* Life.Exp (life expectancy)
* Murder (rate)
* HS.Grad (percentage of high school graduates)
* Frost (mean number of days below freezing in capital city)
* Area

---

## Relationships Between Variables

The pairs function provides a quick look at the relationships between the 8 variables.

```{r, echo=FALSE, fig.height=7, fig.width=7, fig.align='center'}
data(state)
states <- data.frame(state.x77)
pairs(states)
```

--- &twocol

## App Description - Linear Regression

*** =fullwidth
This app allows a user to look more in depth at a particular pair of variables by plotting and summarizing the results of a linear regression.

*** =left
* Input variable: Illiteracy
* Output variable: Life Expectancy
```{r, echo=FALSE}
mdl <- lm(Life.Exp ~ Illiteracy, data=states)
```
```{r}
coef(mdl)
```
```{r}
summary(mdl)$r.squared
```

*** =right
```{r, echo=FALSE, fig.height=6, fig.width=6}
suppressPackageStartupMessages(library(ggplot2))

g <- ggplot(states, aes(x=Illiteracy, y=Life.Exp), height=100) + 
    geom_point(color="red",
               size=5,
               alpha=.5) + 
    ylab("Life Expectancy") +
    xlab("Illiteracy") + 
    ggtitle("Life Expectancy vs Illiteracy") +
    geom_abline(intercept=coef(mdl)[1],
                slope=coef(mdl)[2],
                color="black",
                size=2,
                alpha=.5)
g
```


--- &twocol

## App Description - Prediction

*** =fullwidth
The Shiny app also allows a user to input a value for the variable on the x-axis and predict the outcome for the variable on the y-axis using the linear model.

*** =left
### Input Value for Illiteracy
```{r, echo=FALSE}
inputValue <- 2
inputValue
```
### Predicted Value for Life Expectancy
```{r, echo=FALSE}
prediction <-
    predict(mdl,
            newdata=data.frame(Illiteracy=inputValue))
prediction
```

*** =right
```{r, echo=FALSE, fig.height=6, fig.width=6}
suppressPackageStartupMessages(library(ggplot2))

g <- ggplot(states, aes(x=Illiteracy, y=Life.Exp), height=100) + 
    geom_point(color="red",
               size=5,
               alpha=.5) + 
    ylab("Life Expectancy") +
    xlab("Illiteracy") + 
    ggtitle("Life Expectancy vs Illiteracy") +
    geom_abline(intercept=coef(mdl)[1],
                slope=coef(mdl)[2],
                color="black",
                size=2,
                alpha=.5) +
    geom_point(x=inputValue,
               y=prediction,
               color="black",
               size=5)
g
```
